---
title: Data Cleaning
format: typst
---

<<<<<<< HEAD

```{r}
library(tidyverse)
library(readxl)

rawdata <- read_csv("/Users/brandonbosch/Downloads/gerrymandering-brandongbosch-main/data/g24_sov_by_g24_svprec.csv")

cleaned <- rawdata |>
    mutate(
        COUNTY = as.integer(COUNTY),
        FIPS = as.integer(FIPS),
        SVPREC = as.character(SVPREC),
        ADDIST = as.integer(ADDIST),
        CDDIST = as.integer(CDDIST),
        SDDIST = as.integer(SDDIST),
        BEDIST = as.integer(BEDIST)
    ) |>
        distinct()
write.csv(cleaned, "g24-cleaned.csv")
```
```{r}
library(tidyverse)
library(sf)

srvotes <- rawdata <- read_csv("/Users/brandonbosch/Downloads/gerrymandering-brandongbosch-main/data/g24_sov_by_g24_svprec.csv", show_col_types=FALSE)

rawdata <- read_csv("/Users/brandonbosch/Downloads/gerrymandering-brandongbosch-main/data/g24_sov_by_g24_svprec.csv")
cleaned <- rawdata |>
    mutate(
        COUNTY = as.integer(COUNTY),
        FIPS = as.integer(FIPS),
        SVPREC = as.character(SVPREC),
        ADDIST = as.integer(ADDIST),
        CDDIST = as.integer(CDDIST),
        SDDIST = as.integer(SDDIST),
        BEDIST = as.integer(BEDIST)
    ) |>
        distinct()
write.csv(cleaned, "g24-cleaned.csv")

```
=======
>>>>>>> 6fce489c8c352df656b0a073ccc813cec29c3802
