---
title: Exploratory Data Analysis
format: typst
---

### Question 1

<<<<<<< HEAD
Which precinct had the closest congressional race measured by small absolute difference between US House Democratic and Republican votes
### Answer 1

```{r}
library(tidyverse)

data <- read_csv("g24-cleaned.csv", show_col_types = FALSE) |>
    mutate(
        USPDEM01 = as.numeric(USPDEM01),
        USPREP01 = as.numeric(USPREP01),
        TOTVOTE = as.numeric(TOTVOTE)
    )

closestcd <- data |>
    mutate(cd_margin = abs(USPDEM01 - USPREP01)) |>
    slice_min(cd_margin, n = 1) |>
    select(SVPREC, CDDIST, USPDEM01, USPREP01, cd_margin)

closestcd
```

### Question 2

What is the total number of precincts in California?
### Answer 2

```{r}
library(tidyverse)

data <- read_csv("g24-cleaned.csv")

nprecincts <- nrow(data)
nprecincts
```
### Question 3

What is the range of the total precinct size?
### Answer 3

```{r}
precinctsizerange <- data |>
    summarize(
        min_size = min(TOTVOTE, na.rm = TRUE),
        max_size = max(TOTVOTE, na.rm = TRUE)
    )
    precinctsizerange
```
=======
Put your question here.

### Answer 1

Put your answer here.

### Question 2

Put your question here.

### Answer 2

Put your answer here.

### Question 3

Put your question here.

### Answer 3

Put your answer here.
>>>>>>> 6fce489c8c352df656b0a073ccc813cec29c3802
